CDIPS. I. Light Curves in Open Clusters from TESS Sectors 6 \& 7

### 2019-07-23 paper_I/ms.tex
add paper I
we're splitting it.

paper I: before there were no light curves. now there are some.

paper I: before there were no PCs. now there are some.

\title{
  Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7
}

@@

\begin{abstract}
  % Context
  The Transiting Exoplanet Survey Satellite (TESS) has begun to
  photometrically monitor almost every star cluster in
  the solar neighborhood.
  % Aims
  To make light curves of stars that could be members of stellar
  associations, moving groups, or open clusters, we have begun a
  Cluster Difference Imaging Photometric Survey (CDIPS).
  %
  Our aim is to discover giant transiting planets with known
  ages, and to probe the exoplanet size and separation distributions for
  planets younger than one gigayear.
  %
  In this study, we made \numberlcs light curves of candidate young
  stars, across \numberclusters distinct clusters.
  Each light curve represents between 20 and 25 days of observations
  of a star brighter than $G_{Rp}=16$, sampled at 30 minute cadence.
  % Methods
  We describe in detail the image subtraction and time-series analysis 
  techniques we used to create the light curves, which
  have noise properties that agree with theoretical expectations.
  % Results
  We then highlight the \numberpcs planet candidates we identified in
  an initial search.
  \numberclusterpcs of these planet candidates are candidate cluster
  members, and the remaining \numberzaripcs have indications of youth
  relative to field stars.
  We describe the vetting procedures that these objects have survived,
  and emphasize the additional spectroscopic, photometric, and imaging
  observations that are needed to determine (i) whether these candidates
  are planets and (ii) for which cases the host stars are cluster members.
  %
  We also comment on the possible utility of the light curve sample for
  studies of stellar rotation evolution, and binary eccentricity
  damping.
  %
  The light curves and vetting reports are available at
  \stscilink.
\end{abstract}

@@

Many evolutionary processes are expected to occur over the lives of
stars and exoplanets; it would be interesting to statistically observe
these changes as functions of time.  However, since most dwarf stars
do not appreciably change until evolving off the
main sequence, creative approaches must be used to infer stellar ages
\citep{soderblom_ages_2010}.  One approach beginning to bear fruit in
exoplanet studies is to search for planets in coeval groups of stars,
hereafter ``clusters''.  This includes the open clusters of yore, as
well as the moving groups and stellar associations that began to be
uncovered in the late 1990s \citep{zuckerman_young_2004}.  The ages of
these stellar ensembles are inferred through isochrone analyses of
color-magnitude diagrams, using an appropriate combination of
main-sequence turnoff locations, pre-main-sequence turnon locations,
and averaged MS isochronal ages across known cluster members
\citep[{\it e.g.},][Section 3.4.3]{kharchenko_global_2012}.  Once
calibrated, gyrochronology can also be used to verify the age of a
stellar ensemble \citep[{\it
e.g.},][]{barnes_color-period_2015,meibom_spin-down_2015,curtis_tess_2019}.
The ages of planets discovered in these cluster stars are then assumed
to equal the age of the larger stellar ensemble.

The first planets to be detected in open clusters were found through
radial velocity (RV) measurements of red giants in the Hyades and
NGC~2423 \citep{Sato_et_al_2007,lovis_mayor_2007}.
Subsequent spectroscopic searches in Praesepe led to the detection of
the first hot Jupiter in a cluster \citep{Quinn_et_al_2012}, and also
the first multi-planet system in a cluster \citep{Malavolta_et_al_2016}.
The youngest RV detections have come from surveys of T Tauri stars in the
Taurus star-forming region, which showed signals of the hot Jupiter
\citep[V830~Tau~b][]{donati_hj_2016} and of a giant planet on a 9-day orbit
\citep[CI~Tau~b][]{johns-krull_candidate_2016,flagg_co_2019}.
A final RV survey of note was conducted by
\citet{brucalassi_search_2017}, who followed 88 stars in M~67 over 7
years.  They reported detections of three hot Jupiters around main
sequence stars, and of one giant planet around an evolved star.

The transit method was comparatively slow to catch up.  Deep transit
searches typically comprising days to weeks of observations were
performed for NGC~2158, 6791, and 1245, among other clusters
\citep{mochejska_planets_2005,mochejska_planets_2006,burke_survey_2006}.
Related projects include a search of M~37 by
\citet{hartman_MMT_IV_2009}, of Praesepe by
\citet{pepper_photometric_2008}, and of nine young clusters in the
solar neighborhood by the Monitor team
\citep{aigrain_monitor_2007,irwin_monitordata_2007,miller_monitor_2008}.
Though these studies led to measurements of stellar rotation periods
\citep{hartman_rotation_2009,Irwin_NGC2516_2007} as well as the
discovery of pre-main-sequence (PMS) eclipsing binaries (EBs)
\citep{irwin_monitor_PMSEB_2007}, no definitive transiting planets in
open clusters were found.  Transit searches in globular clusters were
similarly met with null results \citep{gilliland_lack_2000,
weldrake_searching_2006}.  These searches were typically sensitive to
planets larger than Jupiter, on $\lesssim 3$ day orbital periods.  Hot
Jupiter occurrence rate limits were derived at the $\lesssim 5\%$
level \citep[{\it e.g.},][]{burke_survey_2006, hartman_MMT_IV_2009}.
The modern 0.5-1\% occurrence rate suggests that these early transit
surveys needed a greater data volume, at higher precision for
detection to be possible
\citep{mayor_harps_2011,wright_frequency_2012,howard_planet_2012,petigura_metallicity_2018}.

Kepler \citep{borucki_kepler_2010} observed enough stars for long
enough and with sufficient precision to detect transiting planets in
open clusters:  Kepler-66b and 67b, in the gigayear-old NGC~6811
\citep{Meibom_et_al_2013}.  Though a broken reaction wheel ended the
prime Kepler mission, the repurposed K2 \citep{howell_k2_2014}
switched between fields along the ecliptic every quarter-year, and was
able to observe far more clusters and young stars.  The resulting
discoveries made by K2 through its surveys of the Pleiades, Hyades,
Praesepe, and Upper Sco were a major inspiration for the present work.

K2-25b, discovered in the Hyades, has a radius ($3.43\,R_\oplus$) that
is larger than older Kepler planets around M dwarfs at similar insolation levels
\citep{Mann_K2_25_2016}.  This inflated radius is perhaps a hint that
the planet is contracting, or losing its atmosphere \citep[{\it
e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,Fulton_et_al_2017}.  The
super-Neptune sized K2-33b ($P\approx 5.4\,{\rm d}$), found in Upper
Sco, showed that at least some close-in planets must form within about
10 Myr \citep{Mann_K2_33b_2016,David_et_al_2017}.  Further discoveries
included six transiting planets in Praesepe
\citep{obermeier_k2_2016,Mann_et_al_2017}, a long-period candidate
super-Earth in the Hyades \citep{vanderburg_zeitVII_2018}, the
three-planet K2-136 system in the Hyades
\citep{ciardi_k2-136_2018,livingston_three_2018,mann_ZEITVI_2018}, and
later the two-planet system K2-264 in Praesepe
\citep{rizzuto_zeitVIII_2018,livingston_k2-264_2019}.  There has also
recently been a detection by K2 of a Jupiter-sized planet orbiting
every 24 days around V1298~Tau \citep{david_v1298_2019}.

A significant amount of effort continues to be devoted towards the
discovery and characterization of planets around young stars.
Sometimes, cluster membership may not even be necessary, if a star's
youth can be inferred from combined rotation, activity, and kinematic
indicators \citep[{e.g.}, K2-233;][]{david_k2-233_2018}.  To
investigate demographics in time, the detection sensitivities and
reliabilities of these searchers need to be calibrated, likely with a
machinery similar to that outlined by \citet{rizzuto_zeitV_2017}.  A
separate requirement for population studies to be statistically
robust, imposed by the geometric rarity of transits, is that many tens
of thousands of stars with known ages must be monitored at high
precision.

The TESS mission \citep{ricker_transiting_2015}, though designed for
other purposes, holds the promise to deliver the most homogeneous and
comprehensive cluster photometric survey in history.  More
quantitatively, the \citet{Kharchenko_et_al_2013} cluster member
database indicates that $\approx 2\times10^5$ open cluster members
brighter than $T=16$ will be observed in the full-frame images over
the first two years of TESS observations.  This count includes the
``most probable'' members within each cluster's radius, which by the
\citet[][]{kharchenko_global_2012} definition requires the independent
kinematic, photometric, and spatial membership probabilities to each
exceed 61\%.  The actual number of stars in clusters may be larger, as
the membership catalogs are not yet complete, even at these relatively
bright magnitudes \citep[{\it
e.g.},][]{roser_nine_RSG_2016,cantat-gaudin_gaia_2018,cantat-gaudin_newOCs_2019}.
% Our target list currently sits at $\approx 1.0\times10^6$ candidate
% young stars, perhaps one-third of which are bonafide cluster members
% (see \S~\ref{sec:starselection}).

One of the major barriers to deriving precise photometry from the TESS
images is the relatively poor angular resolution ($\approx 21''$ per
pixel).  Almost all clusters are within 10 degrees of the Galactic
plane. The problems with crowding and complex backgrounds are so
severe near the galactic plane that the TESS Candidate Target List has
deprioritized 2-minute targets at galactic latitudes less than
$\approx 15^\circ$~\citep{stassun_TIC_2018,stassun_TIC8_2019}, which
includes almost all star clusters\footnote{TICv8 has updated this to
$10^\circ$, but for the first year of TESS observations, the number
used when selecting target stars was $15^\circ$.}.  This is sensible,
since the large pixel size and the high stellar surface density
make aperture photometry unreliable.  
However, it also means that a
large number of stars in clusters that could yield transiting planets
will go unprocessed by the official {\it TESS} data reduction
pipeline.

@@

By combining difference imaging with forced-aperture photometry, we
can avoid the primary effects of blending.  This is because in
forced-aperture photometry the reference flux is determined from a
calibrated catalog magnitude-to-flux relation.  The deviation from the
reference is measured on the difference image.  Assuming that only a
single source is causing the variability, blended neighbor stars only
act to increase the poisson noise, and down not ``dilute'' transit
signals, down to the angular resoution of the source catalog being
used to determine the reference flux.  This is one of the main
benefits of performing image subtraction in crowded fields.

Of course, not all young stars are in crowded fields.  TESS
observations of a few nearby non-crowded stellar assocations have
already begun bearing fruit, notably DS Tuc Ab (TOI 200;
\citealt{benatti_dstuc_2019,newton_dstuc_2019}), and perhaps the
planet candidates TOI-450 and 451.  These objects are close and
bright, and will be benchmark systems because they are relatively easy
to characterize.  However, statistical studies of how stellar and
planetary properties are affected by ages require tens of thousands of
target stars.  This motivates us to also search the more crowded, and
fainter fields.

We have therefore opted to produce time-series photometry from the
TESS images of any star that could be a member of a coeval group.  We
are also including some stars that we suspect are young due to
combined photometric and astrometric indicators.  We are using the
difference imaging technique because of its benefits in modelling
complex backgrounds in crowded regions.  While we hope to discover at
least a few giant transiting planets, a separate hope is that the
dataset might be useful to those wishing to study the time evolution
of stellar processes.

In the following, \S~\ref{sec:starselection} describes how we selected
target stars. \S~\ref{sec:method} presents the photometric and image
processing methods we used to produce light curves for these stars.
The statistical properties of the \numberlcs light curves from TESS Sectors
6 and 7 are then summarized (\S~\ref{subsec:lcstatistics}).  The
procedure we used to identify and vet transiting planets is
described in \S~\ref{subsec:identifying_ctois}, and the candidate
planets are presented in \S~\ref{subsec:ctois}.
\S~\ref{sec:discussion} discusses the additional work that is required
to confirm or reject the planetary nature of these objects, and
\S~\ref{sec:conclusion} summarizes our findings.

@@

\begin{figure*}[!t]
	\gridline{\fig{mwscmatchstats.pdf}{0.95\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{dias14matchstats.pdf}{0.95\textwidth}{}}
	\vspace{-0.8cm}
	\caption{
		{\it Top.} Quality diagnostics from cross-matching
		\cite{Kharchenko_et_al_2013} cluster members against Gaia-DR2.
		histogram of the distances between matched stars is on the left; a
		histogram of the difference between the true $G$-band magnitude
		and that predicted from 2MASS photometry is in the middle; a scatter
		plot of the same magnitude difference as a function of $G$-band
		magnitude is on the right.
		{\it Bottom.} Same, but cross-matching \cite{dias_proper_2014}
		cluster members to Gaia-DR2.
	}
	\label{fig:xmatch_info}
\end{figure*}

The main aim of the CDIPS project is to increase the number of cluster
stars for which photometric time-series are available, and thereby
facilitate studies of exoplanetary and stellar processes across
different times and stellar environments.  An essential step is
therefore to define a sample of stars that are thought to be young, or
members or clusters, or both.

@@

The probabilistic criteria for inclusion in our target star list is
necessarily heterogeneous across different catalogs.  However, in our
initial stellar selection our aim is completeness, not accuracy.  If
there has been a claim in the literature that a star should be
considered a cluster member, or a young star, we would like to err on
the side of reporting a light curve for the star.  For stars that are
photometrically interesting, we can then perform post-hoc quality
checks using Gaia-DR2 astrometry and photometry to assess cluster
membership and youth.

@@

The well-known algorithms, TFA, Sys-Rem, PDC-MAP, and ARC2, all take
slightly different approaches to constructing this set of basis
vectors, as well as to solving for the weights to assign each linear
component
\citep{kovacs_trend_2005,tamuz_correcting_2005,smith_pdc_2012,aigrain_robust_2017}.
TFA selects individual ``template stars'' as basis vectors, and
equally weights each template when solving for the coefficients via
linear least squares.  PDC-MAP computes ``co-trending basis vectors''
(CBVs) by applying singular value decomposition to the light curves
that show the strongest mutual correlation.  It solves for the
coefficients through a two-step procedure.  The first step is to
calculate the coefficients through linear least squares.  The
least-squares coefficients are then used to construct a prior over
plausible coefficient values, which is then used to recompute the
maximum likelihood coefficients for each star.  This latter step
reduces overfitting for stars with variability not present in the set
of CBVs.

We opted to use two different detrending approaches, each aimed
at a different use case.  For transit-search related science,
we used TFA, as implemented by \texttt{VARTOOLS}
\citep{kovacs_trend_2005,Hartman_Bakos_2016}.  For stellar
astrophysics related work, we used a simple variant of PCA, as
implemented in \texttt{scikit-learn} \citep{sklearn_2011}.  For
self-consistency, we describe each method and its implementation in
the following paragraphs.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{rms_vs_mag.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    Standard deviation of trend-filtered CDIPS light curves as a
    function of catalog TESS-band magnitude.  Black points correspond
    to the minimum RMS across the available three aperture sizes.  The
    model (orange and gray lines) assumes aperture sizes reported by
    \citet{Sullivan_et_al_2015}, and the effective area from
    \citet{vanderspek_2018}.  The noise from unresolved background
    stars (dotted gray line) is a function of galactic latitude, and
    dominates over zodiacal light for faint stars near the galactic
    plane; the line shown assumes a sight-line towards the center of
    Sector 6, Camera 1 (further details are in
    \S~\ref{subsubsec:rmsvsmag}).
		\label{fig:rms_vs_mag}
	}
\end{figure}

@@

\subsection{Identifying Planet Candidates}
\label{subsec:identifying_ctois}

\begin{figure}[!t]
	\gridline{\fig{tls_sde_vs_period_scatter.pdf}{0.45\textwidth}{}}
	\vspace{-0.8cm}
	\caption{
    Transiting planet search periodogram summary.
    Each point represents the TLS periodogram peak signal detection
    efficiency (SDE) and corresponding period from one light curve.
    Significance thresholds (orange lines) are empirically defined for
    the transiting planet search described in
    \S~\ref{subsec:identifying_ctois}.  
    {\it Top.} Sector 6.  {\it Bottom.} Sector 7.
	}
	\label{fig:tlsresults}
\end{figure}

To identify an initial set of transiting planets, strong stellar
rotators, and eclipsing binaries, we performed a few steps of
post-processing on the light curves.  This processing was done
independently of the data release, since it was quite specific to our
own scientific interests.  The code used to do this additional
processing is also available
online\footnote{\url{github.com/lgbouma/cdips}, commit
\texttt{348eea7}.}.

For simplicity, we first chose a single aperture size~--~``aperture
2''~--~with a radius of 1.5  pixels.  Then, to identify periodic
transit-like signals, we used \citet{hippke_TLS_2019}'s transit
least-squares (TLS) tool.  The algorithm is the same as the canonical
box least-squares \citep{kovacs_box-fitting_2002}, except in place of
a box template, a transit template is used  for a marginal improvement
of the detection efficiency.  In addition, the search grids in
\texttt{tls} \footnote{\url{https://github.com/hippke/tls}} are
slightly more efficient than in most BLS implementations, since
\texttt{tls} uses the cubic-in-frequency sampling advocated by
\citet{ofir_optimizing_2014}, rather than standard linear-in-frequency
sampling.  Our grids typically consisted of about 30 different
durations, and about 5000 periods between 0.5 and 21 days.

Before performing the period search, we rejected $6\,{\rm hours}$ at
the beginning and end of each spacecraft orbit, to mitigate the
presence of correlated red noise in the results.  This shrank the data
volume by about 5\%, but also lowered the number of systematic false
positives in subsequent vetting.  We then performed an asymmetric
sigma-clipping of $(50\sigma,5\sigma)$ about the median to preserve
transits while omitting flares and other positive flux excursions.

A number of the light curves show residual variability, often of
stellar origin.  This is expected for a sample of young stars; the
problem of finding transits in the face of large stellar rotation
signals has been explored by both \citet{rizzuto_zeitV_2017} and also
\citet{hippke_wotan_2019}.  The former adopted an approach that we
have yet to explore, which is to pass a sliding window over the light
curve that, within each step, performs a Bayesian model comparison
between a spline and a spline-plus-notch model.  If the
spline-plus-notch model is favored, the transits are preserved for
subsequent discovery.  \citet{hippke_wotan_2019}, conversely,
described a number of different detrending methods, and found that
most performed more or less the same at recovering planetary transits
for a sample of young stars with strong rotation signals.

Our approach in this work is essentially identical to one of the
methods described by \citet{hippke_wotan_2019}.  First, before
sigma-clipping or omitting points near the edges of orbits we run a
generalized Lomb-Scargle periodogram on each TFA light curve
\citep{lomb_1976,scargle_studies_1982,vanderplas_periodograms_2015}.
If a peak is found with false alarm probability below $10^{-5}$, we
consider the star ``variable'', and opt to detrend the flux timeseries
with robust penalized B-splines, which are splines with knot-length
automatically determined via cross-validation
\citep{eilers_flexible_1996}. The idea behind the cross-validation is
that more knots leads to smaller residuals on training data, but
larger errors when tested on the entire dataset.  We used the
\texttt{wotan} implementation, which is a wrapper to the
\texttt{pyGAM} spline fitter, with $2\sigma$ clipping of outliers from
the fit residuals at each iteration
\citep{serven_pygam_2018_1476122,hippke_wotan_2019}.  The maximum
number of spline knots is set to 50, which for each TESS sector
($\approx 25\,{\rm days}$) is commensurate with a $\approx0.5\,{\rm
day}$ window.

We verified by injecting and recovering a 2.5 mmag, zero impact
parameter 
planet with variable period that this detrending approach marginally
improved the recovery probability, compared to not doing anything.
The main cases for which it helps are those with large residual
stellar variability in the TFA light curve.

After (optionally) detrending, we run the TLS search. To select
``significant'' signals for visual inspection, we performed a cut on
the TLS signal detection efficiency defined piecewise over the signal
periods.  The overall lower limit is ${\rm SDE} > 12$, with higher
limits imposed in regions with heavy contamination from systematic
signals.  The signals for sectors 6 and 7 are shown in the space of
SDE vs period in Figure~\ref{fig:tlsresults}.

This yielded a few thousand light curves.  About two-thirds already
had been detrended with splines, and were not processed further.  For
the remaining third we performed TFA signal reconstruction using
\texttt{VARTOOLS}.  In this process, the model lightcurve $A(i)$ in
Equation~\ref{eq:tfa_to_minimize} is set to the phase-binned signal
from the most powerful peak in the TLS spectrum, rather than being a
constant function.  This helps lower the scatter of the light curve at
frequencies away from the TLS peak.

We then make a multi-page \texttt{.pdf}-format document report with
the information necessary to make classifications for vetting.  These
vetting reports are released along with the light curves, and are a
useful summary for anyone interested in the subset of objects that we
have analyzed.  A full description of each page of the report is given
in Appendix~\ref{appendix:vetreport}.
When classifying these reports, we assessed:
\begin{enumerate}
    \item {\it Morphology of photometric variability}. Designations
      include tags for planet candidates, eclipsing binaries,
      instrumental variations, stellar variations, and ``weirdos''.
    %
    \item {\it Cluster membership status}. By default, all light
      curves were made for stars with at least one literature claim of
      cluster membership.  However, some of these claims pre-dated the
      availability of Gaia-DR2 parallaxes or proper motions.  We
      therefore re-assess the membership status on a case-by-case
      basis through inspection of the available astrometry and
      photometry.  Known asterisms are also omitted at this point
      \citep[{\it
      e.g.},][]{sulentic_revised_1973,baumgardt_asterisms_1998,kos_galah_2018}.
    %
    \item {\it Photometric blends}. Tags are created to highlight
      whether the depth of the photometric signal shows a strong
      dependence on aperture size, and also whether the in-transit
      minus the out-of-transit images reveal that the source of
      variability is in fact far from the target star.
\end{enumerate}
The initial classifications were performed by LGB, and possible
planet candidates were then vetted by JH and JNW.
The \texttt{TagSpaces}
software was used to easily assign labels to the documents.

\subsection{Candidate TESS Objects of Interest}
\label{subsec:ctois}

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{quilt_PCs.pdf}
	\end{center}
	\vspace{-0.2cm}
	\caption{
		Phased light curves for six of the \numberpcs candidate
			transiting planets identified in this work.
		Black points are detrended flux measurements, phased to the
		best-fit orbital period indicated in the lower right of each
		panel.
    Transit models are fitted as described in \S~\ref{subsec:ctois},
    and plotted with blue lines.
		For display purposes, a window of $\pm 4$ transit durations
		centered on the transit mid-point is displayed.
		The vetting reports for these objects are available at XXX.	%FIXME
		% TODO: include age? T mag?
		The Gaia source identifiers are
		a): 5605128927705695232, 
		b): 3125263468681400320, 
		c): 5510676828723793920, 
		d): 3007171311355035136, 
		e): 5617126180115568256, 
		f): 3220266049321724416.   
		\label{fig:ctoi_quilt}
	}
\end{figure*}

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{LS_period_vs_color_and_age.pdf}
	\end{center}
	\vspace{-0.2cm}
	\caption{
    Time evolution of Lomb-Scargle periodogram peak period versus Gaia
    color.
		Red stars are on the right, blue stars are on the left.
		Each point on this diagram is a star for which the false alarm
		probability of the most powerful Lomb-Scargle peak is below
		$10^{-15}$.
		Additionally, we required (1) that the membership claim originate
		from \citet{cantat-gaudin_gaia_2018},
		\citet{Kharchenko_et_al_2013}, or \citet{gaia_hr_2018}; and (2)
		that the cluster with claimed membership had an age reported by
		\citet{Kharchenko_et_al_2013}.
		Our approach for avoiding photometric blends is described in
		\S~\ref{subsec:notplanets}.
		\label{fig:ls_peak_vs_time}
	}
\end{figure}

If all vetters identified an object as a planet candidate, we then
proceeded to fit a transit model to the data.  The procedure closely
mirrors that used by \citet{bouma_wasp-4b_2019} to create a
phase-folded light curve for WASP-4.

First, we selected points within 5 transit durations of each transit
midpoint, using the orbital period, transit duration, and reference
epoch found from applying TLS to the detrended light curve.  We then
fitted a line to the out-of-transit flux measurements around each
transit window, and divided it out.  We then fitted a standard transit
model using the formulae given by \citet{mandel_analytic_2002} and
implemented by \citet[][\texttt{BATMAN}]{kreidberg_batman_2015}.  The
free parameters were the orbital period, the reference epoch, the
planet to star radius ratio $R_{\rm p}/R_\star$, the orbital distance
to stellar radius ratio $a/R_\star$, and the inclination $i$.  We
assumed circular orbits.  To fix the quadratic limb-darkening
parameters, we collected $T_{\rm eff}$ and $\log g$ from the TIC, and
then interpolated against the \citet{claret_limb_2017} tables.  For
stars hotter than the maximal effective temperature of these tables
($12,000\,{\rm K}$), we simply used the coefficients of the hottest
star.

>>>>

\title{
  CDIPS. I. Light Curves in Open Clusters from TESS Sectors 6 \& 7
}

@@

\begin{abstract}
  % Context
  The Transiting Exoplanet Survey Satellite (TESS) has begun to
  photometrically monitor almost every star cluster in the solar
  neighborhood.
  % Aims
  Using the TESS images, we have begun a Cluster Difference Imaging
  Photometric Survey (CDIPS), in which we are focusing on stars that
  are candidate cluster members, or else show other indications of
  youth relative to field stars.
  %
  Our aims are to discover giant transiting planets with known
  ages, and also to provide a light curve sample fit for studies in
  stellar astrophysics.
  %
  For this work, we made \numberlcs light curves of candidate young
  stars, across \numberclusters distinct clusters.  Each light curve
  represents between 20 and 25 days of observations of a star brighter
  than $G_{Rp}=16$, sampled at 30 minute cadence.
  % Methods
  We describe the image subtraction and time-series analysis
  techniques we used to create the light curves, which have noise
  properties that agree with theoretical expectations.
  %
  We also comment on the possible utility of the light curve sample for
  studies of stellar rotation evolution, and binary eccentricity
  damping.
  %
  The light curves are available at \stscilink.
\end{abstract}

@@

Each of the $\sim$3000 known star clusters of the Milky Way is a gift
to astrophysics, providing a sample of stars that vary widely in mass
but all have approximately the same age and composition.  Time-series
photometry of clusters has many applications. By measuring rotation
periods over a range of ages, we can study the angular momentum
evolution of stars and improve our ability
to determine stellar ages through gyrochronology \citep[{\it
e.g.},][]{skumanich_time_1972,barnes_color-period_2015,meibom_spin-down_2015,curtis_tess_2019}.
By measuring eccenticities as a function age, we can study the tidal
evolution of binaries (CITE). The detection of eclipsing binaries can
also lead to the precise determination of the absolute dimensions of
the stars and stringent tests of stellar-evolutionary models (CITE).
Finally, transiting exoplanets discovered in clusters can shed light
on the timescales for processes in planet formation, evolution, and
migration \citep[{\it
e.g.},][]{Fortney_et_al_2007,Mann_K2_33b_2016,David_et_al_2017}, as
well as on the effects of metallicity \citep[{\it
e.g.},][]{fischer_planet-metallicity_2005,petigura_metallicity_2018}.

The TESS mission \citep{ricker_transiting_2015}, though designed for
other purposes, holds the promise to deliver the most homogeneous and
comprehensive cluster photometric survey in history.  More
quantitatively, the \citet{Kharchenko_et_al_2013} cluster member
database indicates that $\approx 2\times10^5$ open cluster members
brighter than $T=16$ will be observed in the full-frame images over
the first two years of TESS observations.  This count includes the
``most probable'' members within each cluster's radius, which by the
\citet[][]{kharchenko_global_2012} definition requires the independent
kinematic, photometric, and spatial membership probabilities to each
exceed 61\%.  The actual number of stars in clusters is larger, as the
membership catalogs are not yet complete, even down to these
relatively bright magnitudes \citep[{\it
e.g.},][]{roser_nine_RSG_2016,cantat-gaudin_gaia_2018,cantat-gaudin_newOCs_2019}.

One of the major barriers to deriving precise photometry from the TESS
images is the relatively poor angular resolution ($\approx 21''$ per
pixel).  Almost all clusters are within 10 degrees of the Galactic
plane. The problems with crowding and complex backgrounds are so
severe near the galactic plane that the TESS Candidate Target List has
deprioritizes 2-minute targets at galactic latitudes less than
$\approx 15^\circ$~\citep{stassun_TIC_2018,stassun_TIC8_2019}. This
includes almost all star clusters\footnote{TICv8 has updated the cutoff to
$10^\circ$, but for the first year of TESS observations, the number
used when selecting target stars was $15^\circ$.}.  This is sensible,
since the large pixel size and the high stellar surface density
make aperture photometry unreliable.  
However, it also means that a
large number of stars in clusters that could yield transiting planets
will go unprocessed by the official {\it TESS} data reduction
pipeline.

@@

By combining difference imaging \citep{Alard_Lupton_1998,miller_optimal_2008} 
with forced-aperture photometry, we
can avoid the primary effects of blending.  
In this procedure, the positions of stars are predicted from an 
astrometric solution, while the reference fluxes are determined from a
calibrated catalog magnitude-to-flux relation.  The deviation from the
reference is measured on the difference image.  Assuming that only a
single source is causes the variability, blended neighbor stars only
act to increase Poisson noise, and do not ``dilute'' transit
signals, down to the angular resolution of the source catalog being
used to determine the reference flux.  This is one of the main
benefits of performing image subtraction in crowded fields.

We have therefore opted to produce time-series photometry from the
TESS images of any star that could be a member of a coeval group.  We
are also including some stars that we suspect are young due to
combined photometric and astrometric indicators.  We are using the
difference imaging technique because of its benefits in modelling
complex backgrounds in crowded regions.  While we hope to
discover at least a few giant transiting planets, the focus of the
present study is to produce a more general-purpose dataset,
applicable for studies both in exoplanetary as well as stellar
astrophysics.

For the remainder of this work, we adopt the term ``star cluster'', or
simply cluster, to refer to a coeval group of stars.  This includes
the open clusters of yore, as well as the moving groups and stellar
associations that have been discovered since the late
1990s \citep{zuckerman_young_2004}.

The plan of action is as follows. In \S~\ref{sec:starselection}, we
describe how target stars were selected. \S~\ref{sec:method} presents
the photometric and image processing methods we used to produce light
curves for these stars.  The statistical properties of the \numberlcs
light curves from TESS Sectors 6 and 7 are then summarized
(\S~\ref{subsec:lcstatistics}).  
An example of how we might use the data to identify pulsating
stars, eclipsing binaries, and transiting planets is then
given
(\S~\ref{subsec:identifying_variability}). 
\S~\ref{sec:conclusion}
summarizes our findings, and discusses them with an eye towards
the studies we hope this and subsequent rounds of data processing
will enable.

@@

\begin{figure*}[!t]
	\gridline{\fig{mwscmatchstats.pdf}{0.95\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{dias14matchstats.pdf}{0.95\textwidth}{}}
	\vspace{-0.8cm}
	\caption{
		{\it Top.} Quality diagnostics from cross-matching
		\cite{Kharchenko_et_al_2013} cluster members against Gaia-DR2.
		A histogram of the distances between matched stars is on the left; a
		histogram of the difference between the true $G$-band magnitude
		and that predicted from 2MASS photometry is in the middle; a scatter
		plot of the same magnitude difference as a function of $G$-band
		magnitude is on the right.
		{\it Bottom.} Same, but cross-matching \cite{dias_proper_2014}
		cluster members to Gaia-DR2.
	}
	\label{fig:xmatch_info}
\end{figure*}

The main aim of the CDIPS project is to increase the number of cluster
stars for which photometric time-series are available, and thereby
facilitate studies of exoplanetary and stellar processes across
different times and stellar environments.  A key step is
therefore to define a sample of stars that are thought to be young, or
members of clusters, or both.

@@

The probabilistic criteria for inclusion in our target star list is
necessarily heterogeneous across different catalogs.  However, in our
initial stellar selection we aim for completeness, not accuracy.  If
there has been a claim in the literature that a star should be
considered a cluster member, or a young star, we would like to err on
the side of reporting a light curve for the star.  For stars that are
photometrically interesting, we can then perform post-hoc quality
checks using Gaia-DR2 astrometry and photometry to assess cluster
membership and youth.

@@

The well-known algorithms, TFA, Sys-Rem, PDC-MAP, and ARC2, all take
slightly different approaches to constructing this set of basis
vectors, as well as to solving for the weights to assign each linear
component
\citep{kovacs_trend_2005,tamuz_correcting_2005,smith_pdc_2012,aigrain_robust_2017}.
TFA selects individual ``template stars'' as basis vectors, and
equally weights each template when solving for the coefficients via
linear least squares.  PDC-MAP computes ``co-trending basis vectors''
(CBVs) by applying singular value decomposition to the light curves
that show the strongest mutual correlation.  It solves for the
coefficients through a two-step procedure.  The first step is to
calculate the coefficients through linear least squares.  The
least-squares coefficients are then used to construct a prior over
plausible coefficient values, which is subsequently used to recompute the
maximum likelihood coefficients for each star.  This latter step
reduces overfitting for stars with variability not present in the set
of CBVs.

We opted to use two different detrending approaches, each aimed
at a different use case.  For transit-search related science,
we used TFA, as implemented in \texttt{VARTOOLS}
\citep{kovacs_trend_2005,Hartman_Bakos_2016}.  For stellar
astrophysics related work, we used a simple variant of PCA, as
implemented in \texttt{scikit-learn} \citep{sklearn_2011}.  For
self-consistency, we describe each method and its implementation in
the following paragraphs.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{rms_vs_mag.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    Standard deviation of TFA-detrended CDIPS light curves as a
    function of catalog TESS-band magnitude.  Black points correspond
    to the minimum RMS across the available three aperture sizes.  The
    model (orange and gray lines) assumes aperture sizes reported by
    \citet{Sullivan_et_al_2015}, and the effective area from
    \citet{vanderspek_2018}.  The noise from unresolved background
    stars (dotted gray line) is a function of galactic latitude, and
    dominates over zodiacal light for faint stars near the galactic
    plane; the line shown assumes a sight-line towards the center of
    Sector 6, Camera 1 (further details are in
    \S~\ref{subsubsec:rmsvsmag}).
		\label{fig:rms_vs_mag}
	}
\end{figure}

@@

\subsection{A Few Objects of Interest}
\label{subsec:identifying_variability}

\begin{figure}[!t]
	\gridline{\fig{tls_sde_vs_period_scatter.pdf}{0.45\textwidth}{}}
	\vspace{-0.8cm}
	\caption{
    Transiting planet search periodogram summary.
    Each point represents the TLS periodogram peak signal detection
    efficiency (SDE) and corresponding period from one light curve.
    Significance thresholds (orange lines) are empirically defined for
    the transiting planet search described in
    \S~\ref{subsec:identifying_variability}.  
    {\it Top.} Sector 6.  {\it Bottom.} Sector 7.
	}
	\label{fig:tlsresults}
\end{figure}

We will discuss our search for transiting planets in an upcoming
report.  To identify an initial set of transiting planets, strong
stellar rotators, and eclipsing binaries, we performed a few steps of
post-processing on the light curves.  This processing was done
independently of the data release, since it was quite specific to our
own scientific interests.  The code used to do this additional
processing is also available
online\footnote{\url{github.com/lgbouma/cdips}, commit
\texttt{348eea7}.}.

%FIXME
%FIXME
%FIXME
%FIXME
